\protect Connecting every bit of knowledge: \\ The structure of Wikipedia's First Link Network

### 2016-12-07 writeup/2016-04wikipedia-network/package/wikipedia-network-revtex4-combined.tex
accepted arXiv version

\begin{abstract}
  \protect
  Apples, porcupines, and the most obscure Bob Dylan song---is every topic a few clicks from Philosophy? 
Within Wikipedia, the surprising answer is yes: nearly all 
paths lead to Philosophy.
Wikipedia is the largest, most meticulously indexed collection of human knowledge ever amassed. 
More than information about a topic, Wikipedia is a web of naturally emerging relationships.  
By following the first link in each article, we algorithmically construct a directed network of 
all 4.7 million articles: Wikipedia's First Link Network.
Here, we study the English edition of Wikipedia's First Link Network for insight into how the many 
articles on inventions, places, people, objects, and events are related and organized.  
By traversing every path, we measure the accumulation of first links, path lengths,
groups of path-connected articles, cycles,
and the influence each article exerts in shaping the network.
We find scale-free distributions describe path length, 
accumulation, and influence. Far from dispersed, first links disproportionately accumulate 
at a few articles---flowing from specific to general and culminating around fundamental notions such as
Community, State, and Science. 
Philosophy directs more paths than any other article by two orders of magnitude. 
We also observe a gravitation towards topical articles such as 
Health Care and Fossil Fuel. 
These findings enrich our view of the connections and structure of
Wikipedia's ever growing store of knowledge.

@@

\begin{figure*}[tp!]
  \includegraphics[width=\textwidth]{fig002_traversal_visit_algo_figure.pdf}  
  \caption{
    \textbf{Traversal Visit Algorithm on a sample network.}
     The traversal visit vectors are an adjacency matrix for the paths through the network: 
     the first column indicates the path formed starting with article A. 
     The number of traversal visits for article A is then the number of paths containing A 
     or the sum of the first row in our matrix:
     $\sum_{i=1}^7 A_{\text{visit, i}} = 7$.
  }
  \label{fig:Traversal Visits}
\end{figure*}

Starting at each article, we construct a path through the FLN, 
to map the flow of connections among articles.
The method is order agnostic with respect to which articles are selected first. As long as each article is selected eventually, the resulting metrics are equivalent.
Previous studies have used flow to characterize the structure of river networks
\cite{horton1945erosional, dodds1999unified} and describe the organization of 
blood networks, food systems, and transportation networks
\cite{garlaschelli2003universal}.

@@

While traversal visits measure accumulation, each article's first link also 
influences the shape of the FLN. 
At a point of accumulation, a single article's first link 
can exert great influence over the shape of the FLN by directing many
references on a particular path. To distinguish between an article 
that simply happened to fall within a cycle from an article funneling 
many first links, we develop a second metric called {\it traversal funnels}.
To measure traversal funnels, we traverse the FLN in the same manner as we 
did for traversal visits, but end a path once we enter a cycle.
We are then able to distinguish between an article related to many other ideas
only by virtue of its place in a cycle, from an article exerting influence over where the first links flow. 
In our simple network 
(see Fig.~\ref{fig:Traversal Funnels}), article C 
directs the flow of links towards the 3-cycle, while articles A and B are 
recipients of the flow---without exerting direct influence themselves.

By considering the FLN not only as collection of directly linked pairs of articles, but
as a flow, with accumulated references, cycles, and path-connected groups, we can explore how the many articles in Wikipedia are organized and related.

\section{Results}

\subsection{Degree Distribution}

\begin{figure}[tp!]
  \includegraphics[width=\columnwidth]{fig004_articles_ndegree.pdf}
  \caption{
    \textbf{Highest Ranking Articles by in-degree.}
    We rank each article by the number of direct first links to the article (in-degree). The highest-ranking articles tend to represent geographical and biological abstractions. A full online appendix of the results and data is available \href{http://compstorylab.org/share/papers/ibrahim2016a/index.html}{here}.}
  \label{fig:indegree list}
\end{figure}

\begin{figure}[tp!]
  \includegraphics[width=\columnwidth]{fig005_ndegree_loglog.pdf}
  \caption{
    \textbf{FLN Degree Distribution.}
    We plot the in-degree distribution against rank for all articles with an in-degree of at least 1 on a $\log_{10}-\log_{10}$. We then fit the data to a power law 
    distribution using the Maximum Likelihood Estimator with xmin as the in-degree minimizing Kolmogorov-Smirnov distance. We find xmin to be 5 links with a corresponding power law rank exponent $\alpha \simeq 2.44$ and a size exponent $\gamma \simeq 1.41$.
}
  \label{fig:degree distribution}
\end{figure}

We rank all 11 million articles in the FLN by in-degree to find 
the ``United States'' with 80,249 direct first links as the most referenced
Wikipedia article 
(Fig.~\ref{fig:indegree list}). 
Other high-ranking articles
include foundational abstract concepts such as ``village,'' ``species,''; 
sports associations such as ``American Football,'' ``Association Football''; 
and developed nations such as ``France,'' ``Japan,'' ``Russia,'' ``Australia,'' and 
the ``Netherlands.'' These high ranking articles are useful abstractions: nations
describe a collection of individuals with a common culture, language, or 
geographical proximity; sports teams describe an ever changing collection of 
players often associated with a cultural identity or a geographical 
region. 
Since abstractions such as nations and teams are inherently comprised
of many parts, authors often reference the abstraction when describing a part.

@@

@@

How many links does a connection among articles span? 
We find the longest path length is 365,
corresponding to the yearly calendar of Orthodox Liturgics.
Each day's Liturgics links to the next day's. On the last calendar day, the last article simply links back to January 1, forming a 365-cycle 
(see discussion of cycles ~\ref{cycles}).
We also find similarly lengthy paths following the evolution of a place or topic through time: 
``1953 in Scotland'' or ``1560s Architecture,'' with articles sequentially proceeding by year, decade or era.
In general, the longest paths connect temporally organized ideas.

\begin{figure}[tp!]
  \includegraphics[width=\columnwidth]{fig006_path_lengths_dist.pdf}
  \caption{
    \textbf{Path Length Distribution.}
The network depth appears to have a bimodal distribution with a median of 29 first links in a path.
The 365 cycle for ``Orthodox'' liturgics is the outlier to the right, with historical articles 
describing nations such as ``Scotland'' and ``UK'' also lying outside the third quartile.
More than $75\%$ of articles have path lengths between 
$0$ and $50$ links.}
  \label{fig:Path Length Distribution}
\end{figure}

\begin{figure}[tp!]
  \includegraphics[width=\columnwidth]{fig007_traversals_per_article.pdf} 
  \caption{
    \textbf{Distribution of Traversal Visits.}
    We plot the number of traversal visits for each article by rank on a $\log_{10}-\log_{10}$. We then fit the data to a power law 
    distribution using the Maximum Likelihood Estimator with xmin as the number of traversal visits minimizing Kolmogorov-Smirnov distance. We find xmin to be 866 with a corresponding power law rank exponent $\alpha \simeq 1.72$ and a size exponent $\gamma \simeq 1.58$.
The horizontal flattening around the highest
ranking articles is a result of the cyclic structure (see discussion of Cycles ~\ref{cycles}).
}
  \label{fig:Distribution of Visits}
\end{figure}

\begin{figure}[tp!]
  \includegraphics[width=\columnwidth]{fig008_articles_ranked.pdf}
  \caption{
    \textbf{Highest ranking articles by number of traversal visits.}
We compute the number of traversal visits for each article in the FLN (see 
Sec.~\ref{Traversal Algorithm}). 
In doing so, we can rank each article by the accumulation of first links.
The highest ranking articles by traversal visits reveal where the greatest accumulation occurs.}
  \label{fig:highest visits}
\end{figure}
Of the 11 million articles, 5.5 million had an invalid link or linked back to the same article, yielding a path length of zero. 
This roughly corresponds to the official number of articles on Wikipedia: 
$~4.7$ million as of November 2014---approximately half of the 11 million 
articles in the XML dump are redirects or disambiguations, not full articles.
The most common path length is 29, with $75\%$ of path lengths ranging between 7--30 articles.
As a distribution, more than $75\%$ of articles have a path length below 
$50$ first links 
while a few temporally organized paths exceed 50 links 
(see Fig.~\ref{fig:Path Length Distribution}).

@@

\begin{figure*}[tph!]
  \includegraphics[width=\textwidth]{fig009_2_and_3_cycles.pdf}
  \caption{
    \textbf{Highest ranking 2-cycles and 3-cycles.}
We identify pairs of articles whose first links point to one another, forming
a 2-cycle. We then rank each pair of articles by the total number of 
traversal visits to gauge the most referenced groups of two articles linked
to each other. We find 2-cycles often capture synonyms or articles representing nearly the 
same concepts as opposed to distinct concepts. Similarly, we identify and 
rank 3-cycles to find they appear to capture three closely related ideas or synonyms.}
  \label{fig:cycles}
\end{figure*}
In Fig.~\ref{fig:Distribution of Visits}, we fit traversal visits against a power law distribution using the Maximum Likelihood Estimator with xmin as the number of traversal visits minimizing Kolmogorov-Smirnov distance. We find xmin to be 866 with a corresponding power law rank exponent $\alpha \simeq 1.72$ and a size exponent $\gamma \simeq 1.58$.
We also compared the fit against alternative distributions and found signficiant likelihood ratios favoring a power law fit to an exponential ($R>0, p=2.5\times10^{-60}$) and stretched exponential ($R > 0, p=.0001$).
Similarly to in-degree, we found an inconclusive comparison against a lognormal distribution and a signficiant loglikelihood ratio favoring a truncated power law given the max number of traversal visits is restricted by the number of articles in the FLN. 
On the aggregate, the distribution of traversal visits suggests
a handful of the highest ranking articles contain a disproportionate number of traversal visits, while most have none. The skew in the distribution is not terribly surprising when considering the heuristic of how the links flow: from specific to general.

@@

\subsection{Network Cycles}
\label{cycles}
\begin{figure}[tp!]
  \includegraphics[width=\columnwidth]{fig010_top_funnels.pdf}
  \caption{
    \textbf{Funnels.}
We represent the highest-ranking articles by the number of traversal 
funnels to gauge the influence each article exerts in shaping the 
structure of the FLN. 
We find ``Philosophy'' exerts an overwhelming proportion
of the influence, with other abstract notions and topical concepts ranking
next.}
  \label{fig:Funnels}
\end{figure}

@@

\begin{figure}[tp!]
  \includegraphics[width=\columnwidth]{fig011_funnels_distribution.pdf}
  \caption{
    \textbf{Distribution of Traversal Funnels.}
    We plot the number of traversal funnels for each article by rank on a $\log_{10}-\log_{10}$. We then fit the data to a power law 
    distribution using the Maximum Likelihood Estimator with xmin as the number of traversal visits minimizing Kolmogorov-Smirnov distance. We find xmin to be 30 with a corresponding power law rank exponent $\alpha \simeq 1.73$ and a size exponent $\gamma \simeq 1.58$.
    The outlier on the top left is Philosophy with more traversal funnels than the second highest ranking article by two orders of magnitude.
}
  \label{fig:Funnels Distribution}
\end{figure}

@@

@@

\begin{figure}[tp!]
  \includegraphics[width=\columnwidth]{fig012_popularity_visits.pdf}
  \caption{
\textbf{Article Popularity (by page views) for the highest ranking 1000 articles by traversal visits.}
We use the total number of page views provided by Wikipedia for the month
of October 2015 to compare each article's popularity to traversal visits.
While the most popular articles do not necessarily correspond to the articles
with the highest number of traversal visits, the variation in popularity appears to decrease as the number of traversal visits increases. The greatest number of articles fall within roughly 1 million traversal visits and page views. Overall, the page views for the top 1000 articles articles by traversal visits appear to be log-normally distributed. 
}
  \label{fig:Views and Visits}

\end{figure}
As a distribution, we find few articles influence the structure of the 
FLN. Only $17, 821$ articles have one or more traversal funnels, leaving
more than $99\%$ with none---most articles are recipients of 
the references flowing through the articles with at least one traversal funnel.
When to a power law 
    distribution (using the Maximum Likelihood Estimator) with xmin as the number of traversal funnels minimizing Kolmogorov-Smirnov distance), we find xmin to be 30 with a corresponding power law rank exponent $\alpha \simeq 1.73$ and a size exponent $\gamma \simeq 1.58$
(see Fig.~\ref{fig:Funnels Distribution}). 
When compared against alternative distributions, we find inconclusive results for lognormal and truncated power law distributions and significant log likelihood ratios favoring a power law for exponential ($R>0, p=5.3\times10^{-6}$) and stretched exponential ($R>0, p = 1.8\times10^{-8}$) distributions.
Even within the few articles
influencing the structure of the FLN, only a handful of these exert most of the 
control.

\begin{figure}[tp!]
  \includegraphics[width=\columnwidth]{fig013_popularity_funnels.pdf}
  \caption{
\textbf{Article Popularity (by page views) for the highest ranking 1000 articles by traversal funnels.}
We use the total number of page views provided by Wikipedia for the month
of October 2015 to compare each article's popularity to traversal funnels.
}
  \label{fig:Views and Funnels}
\end{figure}
\subsection{Article Popularity}

@@

While some libraries exist for MediaWiki Markup,
approaches using existing libraries led to several bugs 
including trouble with nested links, nested parenthesis, unclosed tags, escape characters 
as well as compatibility with other libraries used to parse the XML.
Consequently,  we developed an algorithm for parsing the first link in the XML version of each article.
Our parsing algorithm aimed to: 
1) accurately identify the first link among other page elements, and 
2) efficiently do so---that is without needing for several passes through the data.
To process an article in a single pass, we developed a hierarchical system of flags:
\begin{figure}[tp!]
  \includegraphics[width=\columnwidth]{fig014_flags.pdf}  
  \caption{
    \textbf{Parsing Algorithm of Wikipedia's XML dump.}
The highest flag in the hierarchy indicates a Wikimedia template used to mark an element in the side bar, display an image, link to an external file, or another Wikimedia project outside of Wikipeida. Next, to catch any remaining elements outside the main body we have a second flag for <ref>, <div> elements. Finally, we identify parenthesis to ensure we do not capture a link to a pronunciation key.}
  \label{fig:parsing algorithm}
\end{figure}

@@

>>>>

\begin{abstract}
  \protect
  Apples, porcupines, and the most obscure Bob Dylan song---is every topic a few clicks from Philosophy? 
Within Wikipedia, the surprising answer is yes: nearly all 
paths lead to Philosophy.
Wikipedia is the largest, most meticulously indexed collection of human knowledge ever amassed. 
More than information about a topic, Wikipedia is a web of naturally emerging relationships.  
By following the first link in each article, we algorithmically construct a directed network of 
all 4.7 million articles: Wikipedia's First Link Network.
Here, we study the English edition of Wikipedia's First Link Network for insight into how the many 
articles on inventions, places, people, objects, and events are related and organized.

By traversing every path, we measure the accumulation of first links, path lengths,
groups of path-connected articles, and cycles.
We also develop a new method, traversal funnels, to measure the influence each article exerts in shaping the network. 
Traversal funnels provides a new measure of influence for directed networks without spill-over into cycles, in contrast to traditional network centrality measures.
Within Wikipedia's First Link Network, we find scale-free distributions describe path length, 
accumulation, and influence. Far from dispersed, first links disproportionately accumulate 
at a few articles---flowing from specific to general and culminating around fundamental notions such as
Community, State, and Science. 
Philosophy directs more paths than any other article by two orders of magnitude. 
We also observe a gravitation towards topical articles such as 
Health Care and Fossil Fuel. 
These findings enrich our view of the connections and structure of
Wikipedia's ever growing store of knowledge.

@@

\begin{figure*}[tp!]
  \includegraphics[width=\textwidth]{fig002_traversal_visit_algo_figure.pdf}  
  \caption{
    \textbf{Traversal Visit Algorithm on a sample network.}
     The traversal visit vectors are an adjacency matrix for the paths through the network: 
     the first column indicates the path formed starting with article A. 
     The number of traversal visits for article A is then the number of paths containing A 
     or the sum of the first row in our matrix:
     $\sum_{i=1}^7 A_{\text{visit, i}} = 7$.
  }
  \label{fig:Traversal Visits}
\end{figure*}
Starting at each article, we construct a path through the FLN, 
to map the flow of connections among articles.
The method is order agnostic with respect to which articles are selected first. As long as each article is selected eventually, the resulting metrics are equivalent.
Previous studies have used flow to characterize the structure of river networks
\cite{horton1945erosional, dodds1999unified} and describe the organization of 
blood networks, food systems, and transportation networks
\cite{garlaschelli2003universal}. 
In the same vein, we use flow to measure accumulation and develop a new method for isolating influence in a directed network with cycles.

\subsection{Traversal Visits}
\label{Traversal Visits}

@@

\end{figure}
\subsection{Traversal Funnels}
\label{Traversal Funnels}

\begin{figure}[tp!]
  \includegraphics[width=\columnwidth]{fig004_centrality_measures.pdf}
  \caption{
    \textbf{Centrality Measures}
    The table above compares standard centrality measures on the sample network against traversal funnels. While betweenness centrality and eigenvector centrality both reward node A for its place in the cycle, traversal funnels only rewards node C for directing paths into the cycle. }
  \label{fig:Centrality Measures}

While traversal visits measure accumulation, each article's first link also 
influences the shape of the FLN. 
At a point of accumulation, a single article's first link 
can exert great influence over the shape of the FLN by directing many
references on a particular path. To distinguish between an article 
that simply happened to fall within a cycle from an article funneling 
many first links, we develop a second metric called {\it traversal funnels}.
To measure traversal funnels, we traverse the FLN in the same manner as we 
did for traversal visits, but end a path once we enter a cycle.
We are then able to distinguish between an article related to many other ideas
only by virtue of its place in a cycle, from an article exerting influence over where the first links flow. 
In the sample network 
(see Fig.~\ref{fig:Traversal Funnels}), article C 
directs the flow of links towards the 3-cycle, while articles A and B are 
recipients of the flow---without exerting direct influence themselves.

The algorithm increments the traversal funnels count along each path, up to the start of a cycle. The resulting count is each node's number of traversal funnels: the number of paths the node directs up to the start of a cycle. Below is the pseudo-code.

\begin{verbatim}
Traversal Funnels Algorithm

// 1. Determine Cycles 
for node in Graph
    next_node = node.link
    visited = {node, next_node}
    // advance to potential cycle
    while next_node not in visited:
        next_node = next_node.link
        visited.add(next_node)
    // mark cycle
    if (node == next_node):
        node.in_cycle = True

// 2. Compute Traversal Funnels
for node in Graph:
    while node.in_cycle == False:
        node.funnels += 1
        node = node.link
\end{verbatim}

The algorithm's average runtime is proportional to the product of the number of nodes, $n$, and the average path length, $l$. If the average path length is fixed (independent of $n$), the runtime is $O(n)$ with $O(n + l)$ auxiliary memory for storing cycles and traversing paths. In the worst case where $l$ is proportional to $n$, the runtime is $O(n^2)$ with $O(n)$ auxiliary memory for storing cycles and traversing paths. In implementation, each iteration step in the algorithm can be parallelized since the algorithm is order agnostic, as long as each node is eventually selected.

As a measure of influence, traversal funnels differs from traditional centrality measures such as degree centrality, betweenness centrality, and eigenvector centrality. 
Degree centrality characterizes how many articles have a first link to a particular topic, restricting influence to a single link. 
Betweenness centrality and eigenvalue centrality capture flow within the network more than a single link away. 
Unlike traversal funnels however, betweenness centrality and eigenvalue centrality reward nodes that simply happen to be in a cycle. 
We compute betweenness centrality and eigenvalue centrality on the sample network using \href{https://networkx.github.io/}{NetworkX}, a Python package for modelling complex networks (see the \href{http://compstorylab.org/share/papers/ibrahim2016a/index.html}{online appendix} for details). 
In our sample network (see Fig.~\ref{fig:Centrality Measures}), node A has betweenness centrality of 0.17 and eigenvalue centrality of 0.58, although node A is simply the recipient of paths directed by node C.
Eigenvector centrality even assigns the same centrality to nodes A, B, and C.

In contrast, traversal funnels defines a path without a predetermined end node, following the progression of links to its culmination at the start of a cycle. Furthermore, traversal funnels provides an interpretable metric: a node's traversal funnels is the number of paths the node directs to the start of a cycle. 
Consequently, traversal funnels allow us to isolate the paths directed by node C, of which there are 4, without any spill over effect on other nodes in its cycle: A and B have zero traversal funnels.

In addition, traversal funnels extends to directed networks with more than one outward edge. In such a network, there may be multiple paths associated with a single starting node. 
The same interpretation for traversal funnels as the number of paths a node directs to a cycle still holds. 
In contrast to betweenness centrality, traversal funnels would not favor the shortest path over any other. Traversal funnels equally weighs all paths up to a cycle.

By considering the FLN not only as collection of directly linked pairs of articles, but
as a flow using traversal funnels, with accumulated references, cycles, and path-connected groups, we explore how the many articles in Wikipedia are organized and related.

\section{Results}
\subsection{Degree Distribution}

\begin{figure}[tp!]
  \includegraphics[width=\columnwidth]{fig005_articles_ndegree.pdf}
  \caption{
    \textbf{Highest Ranking Articles by in-degree.}
    We rank each article by the number of direct first links to the article (in-degree). The highest-ranking articles tend to represent geographical and biological abstractions. A full online appendix of the results and data is available \href{http://compstorylab.org/share/papers/ibrahim2016a/index.html}{here}.}
  \label{fig:indegree list}
\end{figure}
We rank all 11 million articles in the FLN by in-degree to find 
the ``United States'' with 80,249 direct first links as the most referenced
Wikipedia article 
(Fig.~\ref{fig:indegree list}). 
Other high-ranking articles
include foundational abstract concepts such as ``village,'' ``species,''; 
sports associations such as ``American Football,'' ``Association Football''; 
and developed nations such as ``France,'' ``Japan,'' ``Russia,'' ``Australia,'' and 
the ``Netherlands.'' These high ranking articles are useful abstractions: nations
describe a collection of individuals with a common culture, language, or 
geographical proximity; sports teams describe an ever changing collection of 
players often associated with a cultural identity or a geographical 
region. 
Since abstractions such as nations and teams are inherently comprised
of many parts, authors often reference the abstraction when describing a part.

@@

\begin{figure}[tp!]
  \includegraphics[width=\columnwidth]{fig006_ndegree_loglog.pdf}
  \caption{
    \textbf{FLN Degree Distribution.}
    We plot the in-degree distribution against rank for all articles with an in-degree of at least 1 on a $\log_{10}-\log_{10}$. We then fit the data to a power law 
    distribution using the Maximum Likelihood Estimator with xmin as the in-degree minimizing Kolmogorov-Smirnov distance. We find xmin to be 5 links with a corresponding power law rank exponent $\alpha \simeq 2.44$ and a size exponent $\gamma \simeq 1.41$.
}
  \label{fig:degree distribution}
\end{figure}

@@

\begin{figure}[tp!]
  \includegraphics[width=\columnwidth]{fig007_path_lengths_dist.pdf}
  \caption{
    \textbf{Path Length Distribution.}
The network depth appears to have a bimodal distribution with a median of 29 first links in a path.
The 365 cycle for ``Orthodox'' liturgics is the outlier to the right, with historical articles 
describing nations such as ``Scotland'' and ``UK'' also lying outside the third quartile.
More than $75\%$ of articles have path lengths between 
$0$ and $50$ links.}
  \label{fig:Path Length Distribution}
\end{figure}
How many links does a connection among articles span? 
We find the longest path length is 365,
corresponding to the yearly calendar of Orthodox Liturgics.
Each day's Liturgics links to the next day's. On the last calendar day, the last article simply links back to January 1, forming a 365-cycle 
(see discussion of cycles ~\ref{cycles}).
We also find similarly lengthy paths following the evolution of a place or topic through time: 
``1953 in Scotland'' or ``1560s Architecture,'' with articles sequentially proceeding by year, decade or era.
In general, the longest paths connect temporally organized ideas.

Of the 11 million articles, 5.5 million had an invalid link or linked back to the same article, yielding a path length of zero. 
This roughly corresponds to the official number of articles on Wikipedia: 
$~4.7$ million as of November 2014---approximately half of the 11 million 
articles in the XML dump are redirects or disambiguations, not full articles.
The most common path length is 29, with $75\%$ of path lengths ranging between 7--30 articles.
As a distribution, more than $75\%$ of articles have a path length below 
$50$ first links 
while a few temporally organized paths exceed 50 links 
(see Fig.~\ref{fig:Path Length Distribution}).

\begin{figure}[tp!]
  \includegraphics[width=\columnwidth]{fig008_traversals_per_article.pdf} 
  \caption{
    \textbf{Distribution of Traversal Visits.}
    We plot the number of traversal visits for each article by rank on a $\log_{10}-\log_{10}$. We then fit the data to a power law 
    distribution using the Maximum Likelihood Estimator with xmin as the number of traversal visits minimizing Kolmogorov-Smirnov distance. We find xmin to be 866 with a corresponding power law rank exponent $\alpha \simeq 1.72$ and a size exponent $\gamma \simeq 1.58$.
The horizontal flattening around the highest
ranking articles is a result of the cyclic structure (see discussion of Cycles ~\ref{cycles}).
}
  \label{fig:Distribution of Visits}
\end{figure}

\begin{figure}[tp!]
  \includegraphics[width=\columnwidth]{fig009_articles_ranked.pdf}
  \caption{
    \textbf{Highest ranking articles by number of traversal visits.}
We compute the number of traversal visits for each article in the FLN (see 
Sec.~\ref{Traversal Algorithm}). 
In doing so, we can rank each article by the accumulation of first links.
The highest ranking articles by traversal visits reveal where the greatest accumulation occurs.}
  \label{fig:highest visits}
\end{figure}

@@

\begin{figure*}[tph!]
  \includegraphics[width=\textwidth]{fig010_2_and_3_cycles.pdf}
  \caption{
    \textbf{Highest ranking 2-cycles and 3-cycles.}
We identify pairs of articles whose first links point to one another, forming
a 2-cycle. We then rank each pair of articles by the total number of 
traversal visits to gauge the most referenced groups of two articles linked
to each other. We find 2-cycles often capture synonyms or articles representing nearly the 
same concepts as opposed to distinct concepts. Similarly, we identify and 
rank 3-cycles to find they appear to capture three closely related ideas or synonyms.}
  \label{fig:cycles}
\end{figure*}
In Fig.~\ref{fig:Distribution of Visits}, we fit traversal visits against a power law distribution using the Maximum Likelihood Estimator with xmin as the number of traversal visits minimizing Kolmogorov-Smirnov distance. We find xmin to be 866 with a corresponding power law rank exponent $\alpha \simeq 1.72$ and a size exponent $\gamma \simeq 1.58$.
We also compared the fit against alternative distributions and found signficiant likelihood ratios favoring a power law fit to an exponential ($R>0, p=2.5\times10^{-60}$) and stretched exponential ($R > 0, p=.0001$).
Similarly to in-degree, we found an inconclusive comparison against a lognormal distribution and a signficiant loglikelihood ratio favoring a truncated power law given the max number of traversal visits is restricted by the number of articles in the FLN. 
On the aggregate, the distribution of traversal visits suggests
a handful of the highest ranking articles contain a disproportionate number of traversal visits, while most have none. The skew in the distribution is not terribly surprising when considering the heuristic of how the links flow: from specific to general.

@@

\subsection{Network Cycles}
\label{cycles}

@@

\begin{figure}[tp!]
  \includegraphics[width=\columnwidth]{fig011_top_funnels.pdf}
  \caption{
    \textbf{Funnels.}
We represent the highest-ranking articles by the number of traversal 
funnels to gauge the influence each article exerts in shaping the 
structure of the FLN. 
We find ``Philosophy'' exerts an overwhelming proportion
of the influence, with other abstract notions and topical concepts ranking
next.}
  \label{fig:Funnels}
\end{figure}

@@

\begin{figure}[tp!]
  \includegraphics[width=\columnwidth]{fig012_funnels_distribution.pdf}
  \caption{
    \textbf{Distribution of Traversal Funnels.}
    We plot the number of traversal funnels for each article by rank on a $\log_{10}-\log_{10}$. We then fit the data to a power law 
    distribution using the Maximum Likelihood Estimator with xmin as the number of traversal visits minimizing Kolmogorov-Smirnov distance. We find xmin to be 30 with a corresponding power law rank exponent $\alpha \simeq 1.73$ and a size exponent $\gamma \simeq 1.58$.
    The outlier on the top left is Philosophy with more traversal funnels than the second highest ranking article by two orders of magnitude.
}
  \label{fig:Funnels Distribution}
\end{figure}

@@

As a distribution, we find few articles influence the structure of the 
FLN. Only $17, 821$ articles have one or more traversal funnels, leaving
more than $99\%$ with none---most articles are recipients of 
the references flowing through the articles with at least one traversal funnel.
When to a power law 
    distribution (using the Maximum Likelihood Estimator) with xmin as the number of traversal funnels minimizing Kolmogorov-Smirnov distance), we find xmin to be 30 with a corresponding power law rank exponent $\alpha \simeq 1.73$ and a size exponent $\gamma \simeq 1.58$
(see Fig.~\ref{fig:Funnels Distribution}). 
When compared against alternative distributions, we find inconclusive results for lognormal and truncated power law distributions and significant log likelihood ratios favoring a power law for exponential ($R>0, p=5.3\times10^{-6}$) and stretched exponential ($R>0, p = 1.8\times10^{-8}$) distributions.
Even within the few articles
influencing the structure of the FLN, only a handful of these exert most of the 
control.

\subsection{Article Popularity}

\begin{figure}[tp!]
  \includegraphics[width=\columnwidth]{fig013_popularity_visits.pdf}
  \caption{
\textbf{Article Popularity (by page views) for the highest ranking 1000 articles by traversal visits.}
We use the total number of page views provided by Wikipedia for the month
of October 2015 to compare each article's popularity against traversal visits.
Overall, more page views do not correspond to higher traversal visits---Wikipedia users do not tend to visit articles with a higher accumulation in the FLN more so than they visit others. 
However, the variation in popularity appears to decrease as the number of traversal visits increases. The greatest number of articles fall within roughly 1 million traversal visits and page views. Furthermore, page views for the top 1000 articles articles by traversal visits appear to be log-normally distributed. 
}
  \label{fig:Views and Visits}

\end{figure}
\begin{figure}[tp!]
  \includegraphics[width=\columnwidth]{fig014_popularity_funnels.pdf}
  \caption{
\textbf{Article Popularity (by page views) for the highest ranking 1000 articles by traversal funnels.}
We use the total number of page views provided by Wikipedia for the month
of October 2015 to compare each article's popularity to traversal funnels.
Similar to traversal visits, more page views do not correspond to higher traversal funnels---Wikipedia users do not tend to visit articles with a higher influence in the FLN more so than they visit others.
}
  \label{fig:Views and Funnels}
\end{figure}

@@

While some libraries exist for MediaWiki Markup,
approaches using existing libraries led to several bugs 
including trouble with nested links, nested parenthesis, unclosed tags, escape characters 
as well as compatibility with other libraries used to parse the XML.
Consequently,  we developed an algorithm for parsing the first link in the XML version of each article.
Our parsing algorithm aimed to: 
1) accurately identify the first link among other page elements, and 
2) efficiently do so---that is without needing for several passes through the data.
To process an article in a single pass, we developed a hierarchical system of flags:
\begin{figure}[tp!]
  \includegraphics[width=\columnwidth]{fig015_flags.pdf}  
  \caption{
    \textbf{Parsing Algorithm of Wikipedia's XML dump.}
The highest flag in the hierarchy indicates a Wikimedia template used to mark an element in the side bar, display an image, link to an external file, or another Wikimedia project outside of Wikipeida. Next, to catch any remaining elements outside the main body we have a second flag for <ref>, <div> elements. Finally, we identify parenthesis to ensure we do not capture a link to a pronunciation key.}
  \label{fig:parsing algorithm}
\end{figure}

@@

\bibitem{xefer2011philosophy}
.~Xefer, May.
\newblock All road lead to philosophy.
\newblock [Online; accessed 22-April-2016].
